Data_Processing

### 2021-04-20 Code/Data_Processing.Rmd
commit_EH
Data Processing updates

#### Attempted code: Trying to fill in the missing values with previous value - doesn't work with a list/string
#IV_tracklogs_ascending1 <- 
#  IV_tracklogs_ascending %>% 
#  fill(use, use, .direction = 'down')

@@

# If the "use" column in IV_tracklogs_ascending is blank then the details previously recorded remained the same; Therefore, need to fill in blanks with previously recorded value for use_cha and use_num columns
IV_tracklogs_ascending <- 
  IV_tracklogs_ascending %>% 
  fill(use_cha, use_cha, .direction = 'down') %>% 
  fill(use_num, use_num, .direction = 'down')

### Attempted code to fill use_num with blanks where use doesnt have a character and fill with previous number when it does. 
# ifelse(IV_tracklogs_ascending$use != "[0-9]+", IV_tracklogs_ascending$use_num == "", fill(use_num, use_num, .direction = 'down'))

@@

>>>>

# If the "use" column in IV_tracklogs_ascending is blank then the details previously recorded remained the same; Therefore, need to fill in blanks with previously recorded value; Need to fill cells of empty strings with NA first before filling
IV_tracklogs_ascending <-
  IV_tracklogs_ascending %>% 
  mutate(use = if_else(use=="", NA_character_,use)) %>% 
  fill(use, .direction = "down")

@@

@@

## Saving Processed Datasets

```{r}

write.csv(IV_tracklogs_ascending, row.names = FALSE, file = "./Data/Processed/IV_tracklogs_processed.csv")

write.csv(IV_wpts_ascending, row.names = FALSE, file = "./Data/Processed/IV_wpts_processed.csv")
